COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2019-12-17 main.tex
Rework discussion of figure 4

Next, we move on to examine the statistics of the collisions that occur. Figure \ref{fig:coll_hist_a} shows the distribution of semimajor 
axes of every collision that is resolved. Here, the semimajor axis of a collision is defined as the semimajor axis of the first body 
participating in the collision at the moment that it occurs. During a collision, the determination of which body is first and which is 
second is determined by the collision search tree in {\sc ChaNGa}. To ensure that this does not introduce any bias, we also 
constructed figure \ref{fig:coll_hist_a} using the orbital parameters of the second body and found no qualitative difference. By 
examining the semimajor axis distribution of the collisions, it is easy to see how the MMRs affect the collision rates. The dashed lines 
again represent the libration width of each resonance and are meant to show its range of influence. In both the circular and eccentric 
Jupiter simulations, the collision rate is clearly enhanced interior to the 2:1 MMR. The 3:1 MMR only appears to have a noticeable 
influence on the collision rate in the EJ simulation. In both cases, although the 5:3 MMR has a clear influence on the on the 
semimajor-axis eccentricity distribution, it does not leave a measureable imprint on the collision rate. It is important to point out, 
however, that the libration width of sufficiently eccentric particles near the 5:3 MMR may extend beyond the outer edge of the disk 
and introduce boundary effects.

Although the semimajor axis of a particle at the moment of collision provides useful information about how the mean motion 
resonances affect the collision rate in the disk, this information alone is not enough to predict where the second generation dust that 
is produced will end up. To do so, we will operate under the assumption that dust grains produced by collision events will quickly 
couple to the gas and attain a circular orbit. This assumption, which will be further justified in section \ref{sec:dust}, allows to map the 
radial variation in the dust surface density to the radial position of the collisions. This is shown in figure \ref{fig:coll_hist_r}, where the 
histograms indicate the x and y coordinates of a body at the moment that it undergoes a collision.

>>>>

Figure \ref{fig:coll_hist_a} shows the semimajor axis of collisions resolved in the CJ (top) and EJ simulations (bottom). The 
'semimajor axis of a collision' is defined as the semimajor axis of the first of the two planetesimals participating in a collision at the 
moment that it happens. To ensure that the definition of the first and second collider chosen by {\sc ChaNGa} does not influence 
these results, we also tried constructing figure \ref{fig:coll_hist_a} using the second collider and found no qualitative differences. 
Although both simulations were integrated and collisions were resolved for 5,000 years, we only show collisions that occurred during 
the last 3,000 years of the simulations. Before this time, the resonant features in the semimajor axis-eccentricity distribution (see 
figure \ref{fig:ae}) were still developing and had not yet reached a steady state. This results in transient features appearing in the 
collision profiles early on, which we exclude from figure \ref{fig:coll_hist_a} and all subsequent figures.

Most notably, the MMRs appear to have a measurable effect on the local collision rates. Slightly interior to the 2:1 resonance, the 
collision rate increases by a factor of roughly 2. In the EJ simulation, there is a significant deficiency in the number of collisions near 
the 3:1 MMR. We attribute this to the fact that the strength of a second order MMR scales as $e^{2}$, while a first order MMR scales 
linearly. Therefore, one would expect the 3:1 resonance to have more of an influence on the collision rate in a secularly perturbed 
disk. Although viewing the collision rate as a function of semimajor axis allows one to see a clear connection between the 
resonances and the collision rate, this does not immediately indicate where the dust generated by collisions will end up in the disk.

%Next, we move on to examine the statistics of the collisions that occur. Figure \ref{fig:coll_hist_a} shows the distribution of semimajor axes of every collision that is resolved. Here, the semimajor axis of a collision is defined as the semimajor axis of the first body participating in the collision at the moment that it occurs. During a collision, the determination of which body is first and which is second is determined by the collision search tree in {\sc ChaNGa}. To ensure that this does not introduce any bias, we also constructed figure \ref{fig:coll_hist_a} using the orbital parameters of the second body and found no qualitative difference. By examining the semimajor axis distribution of the collisions, it is easy to see how the MMRs affect the collision rates. The dashed lines again represent the libration width of each resonance and are meant to show its range of influence. In both the circular and eccentric Jupiter simulations, the collision rate is clearly enhanced interior to the 2:1 MMR. The 3:1 MMR only appears to have a noticeable influence on the collision rate in the EJ simulation. In both cases, although the 5:3 MMR has a clear influence on the on the semimajor-axis eccentricity distribution, it does not leave a measureable imprint on the collision rate. It is important to point out, however, that the libration width of sufficiently eccentric particles near the 5:3 MMR may extend beyond the outer edge of the disk and introduce boundary effects.

%Although the semimajor axis of a particle at the moment of collision provides useful information about how the mean motion resonances affect the collision rate in the disk, this information alone is not enough to predict where the second generation dust that is produced will end up. To do so, we will operate under the assumption that dust grains produced by collision events will quickly couple to the gas and attain a circular orbit. This assumption, which will be further justified in section \ref{sec:dust}, allows to map the radial variation in the dust surface density to the radial position of the collisions. This is shown in figure \ref{fig:coll_hist_r}, where the histograms indicate the x and y coordinates of a body at the moment that it undergoes a collision.
